\begin{thanks}
This thesis is the result of many years of study whereby I have been accompanied and supported by many people. It is a pleasure to convey my gratitude to all of them in my humble acknowledgement.

I want to give my sincerely thanks to my graduation designation supervisor Prof. Jingzhi Li for his earnest guidance and great help during my undergraduate study at SUSTC.

I would especially like to recognize my academic supervisors, Prof. Xianke Zhang and Prof. Jietai Yu, who have always given me encouragements and confidence in myself. They have played important roles in my decision to continue my education and inspired me for what I could achieve in the future. During the preparation of the thesis, we had many fruitful discussion. They have given me so many advises on the details of the thesis, including the tentative methods and writing techniques etc.

I am very grateful for all the encouragement I have received from my family and from a network of friends.  I would also like to thank my wonderful committee of professors. The committee members Prof. Xianke Zhang, Prof. Jingzhi Li, Prof. Anyue Chen, Prof. Xuejun Jiang and Prof. Linlin Su, who have contributed to the completion of this thesis through their guidance and exceptional teaching, which have helped me get through my education this far.  


Finally, I'd like to say thanks to all my teachers in SUSTC, especially teachers in the Department of Financial Mathematics for providing a stimulating environment. I am very grateful for all the encouragement I have received from my family and from a network of friends. 



\vskip 18pt

\begin{flushright}

Wenchao Zhang

September,2014

\end{flushright}

\end{thanks}
